With the agile methodologies being applied within companies of bigger sizes than its methodologies were originally designed for, any case study in the area of large scale agile eventually contributes to the existing body of knowledge. This thesis focused on the belated integration difficulties related to information and communication flow within the organisation and their implicative affect on the working environment of the \acp{XFT}. In an organisation faced with problematic information search, evaluation, information distortion and overflow their interplay with the challenges of communication islands, bottlenecks, geographical distribution and perspective differences influences the organisational balances and forces. Adjusting the level of organisational transparency and the related trade-offs of \acp{XFT} empowerment and work flow is a step influencing the productivity characteristics of the development teams. The study concludes, that seemingly secondary to software development, areas of communication and information flow within the organisation are the integral aspects to consider within the adoption of a new way of working.

\section{Future Work}

Despite having only one case, the study opens avenues for future research.
As a consequence of research on agile software development from a perspective focusing on communication and information being sparse \citep{pikkarainen2008impactagilecommunication}, this study intended to impart a structured understanding surrounding it. Just as \citet{badampudi2013proddelay} unfolds potential productivity delays the study attempts to integrate independently discovered determinants into a bigger picture of forces and balances.

This comprehension calls for \emph{(i)} a more profound relation of communication and information challenges to be developed. On the given basis one could also more extensively \emph{(ii)} determine causes of productivity determinants to different trade-off positionings. Furthermore, \emph{(iii)} conducting a survey for constructing heat maps and social networks with more \acp{XFT} holds potential to bring forth profound and more diverse findings. 