\chapter{Limitations}

\section{Delimitations}

Only one case study will be performed during the thesis due to a limited amount of available resources. Interviews will be of different lengths depending on the interviewees role within the organisations. The interviews content will be guided by results from surveys as performed with two groups before the interviews started. This tries to align both the quantitative and qualitative threat within the case study. 
Further a through investigation or even an application of existing maturity models in the context of agile development process will not be performed. The case study rather focusses on communication flow and types within the organizational structure. No new measurements will be introduced and collected due to a limited time-frame of the study not allowing to observe any reliable trends. The sole performance of \ac{XFT}s will not be assessed and literature related to this subject will not be reviewed as it was not identified as a problematic area of the development process by Ericsson PDU LMR/Configuration and O\&M.

\section{Addressed threats to validity}

%Should be later on incorporated with the threats
Both researchers participated in the transcribing and following coding of the interviews thereby increasing the consistency of the process. After the interviews were transcribed, they were demonstrated to the respondents allowing them to point out any discrepancies in interpretation thus minimizing the risk of subjective judgement and resulting distortion of information by the researchers.
The interviewees were drawn from different areas in the organizational structure to assure variety in perspectives on the issue and thus increase the possibility of discovering more potential problems pertaining to certain areas of responsibility. As the access to potential respondents was limited to two~\ac{XFT}s and their managerial environment the obtained results are weakened by the shortcomings of convenience sampling. The sample does not claim to be statistically significant and observed results must be processed with the acknowledgement of potential bias.

%The interviews were designed in accordance to guide A and guide B and piloted with X people to assure the consistency of the interview design and eliminate ambiguousness of questions.

